Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-10-11 HGmodelMANUSCRIPT/REPLYtoREVIEWER2.txt

Reviewer 2.

We thank for the very positive feedback. The errors in English are
now fixed as suggested.

Reviewer 1.

@@

1.
Author reply:

2.
Author reply:

All the "subjective sweet spots" in Fig. 2 have exactly the same size: 0.04 units.

This size was agreed on based on the high experimental repeatibility of the order
parameters that we discuss in the text (p12): "Almost all the reported values are
within a variation of ±0.02 [...] for all fully hydrated PC bilayers, regardless
of the variation in their acyl chain composition and temperature."

To make the (equal) size of the sweet spots clear to the reader, we now explicitly
point out this size when introcuding them in the text (p15):

Motivated by the high experimental reproducibility, we have highlighted in Fig. 2
the subjective sweet spots (light blue areas **spanning 0.04 units**), within which
we expect the calculated absolute values of the order parameters of a well-performing
force field to fall.

The added words are those between the stars (**).

### 2015-10-11 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Added explicitly the size of the subjective sweet spots.

In general there is a good agreement between the order parameters measured with different experimental NMR techniques: Almost all the 
reported values are within a variation of $\pm$0.02 (which is also the error estimate given by Gross et al.~\cite{gross97}) 
for all fully hydrated PC bilayer, regardless of the variation in their acyl chain composition and temperature.
Exceptions are the somewhat lower order parameters sometimes reported from measurements using $^1$H-$^{13}$C NMR~\cite{hong95a,hong95b,warschawski05}.
These experiments are not shown in Fig.~\ref{HGorderparameters} as the reported error bars are either relatively large~\cite{hong95a,hong95b}, 
or the spectral resolution is quite low and the numerical lineshape simulations have not been used in the analysis~\cite{warschawski05}.
Due to this end, it is highly likely that these reported lower order parameters are due to lower experimental 
accuracy and therefore we exclude them from our discussion. 
For more details, see Ref.~\citenum{accuracyPOST}. 
Motivated by the high experimental reproducibility, we have highlighted in 
Fig.~\ref{HGorderparameters} the subjective sweet spots (light blue areas), within which we expect the calculated absolute 
values of the order parameters of a well-performing force field to fall.

>>>>

In general there is a good agreement between the order parameters measured with different experimental NMR techniques: Almost all the 
reported values are within a variation of $\pm$0.02 (which is also the error estimate given by Gross et al.~\cite{gross97}) 
for all fully hydrated PC bilayers, regardless of the variation in their acyl chain composition and temperature.
Exceptions are the somewhat lower order parameters sometimes reported from measurements using $^1$H-$^{13}$C NMR~\cite{hong95a,hong95b,warschawski05}.
These experiments are not shown in Fig.~\ref{HGorderparameters} as the reported error bars are either relatively large~\cite{hong95a,hong95b}, 
or the spectral resolution is quite low and the numerical lineshape simulations have not been used in the analysis~\cite{warschawski05}.
Due to this end, it is highly likely that these reported lower order parameters are due to lower experimental 
accuracy and therefore we exclude them from our discussion. 
For more details, see Ref.~\citenum{accuracyPOST}. 
Motivated by the high experimental reproducibility, we have highlighted in 
Fig.~\ref{HGorderparameters} the subjective sweet spots (light blue areas spanning 0.04 units), within which we expect the calculated absolute 
values of the order parameters of a well-performing force field to fall.
